---
title: 'Wilmington Voters'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Create filtering of registration sorting by:**

1. ED and RD
2. And also include Wilmington Housing Authority high-rises and properties 
* This would be a separate address list
3. Exclude non-voters by sorting by the date the person last voted with the intent to exclude non-voters (defined as someone who hasn’t voted for 4+ years, meaning if someone last voted in 2014, they’re a non-voter)
* But including those who recently registered since November 2016 but have not had the time to vote in a Presidential election
4. Sort by political party (D, R, and other)
5. Sort by if someone is a consistent primary voter, or only votes in a general election


```{r}
# install.packages("here")
library(here)

# install.packages("tidyverse")
library(tidyverse)

# install.packages("readxl")
library(readxl)

# install.packages("janitor")
library(janitor)
```

```{r}
# Read data from Excel
voters <- read_xlsx(here::here("ActiveFile-Wilm1thru8-20191015.xlsx"))
```

```{r}
# Check column names
colnames(voters)

# Remove characters (such as "-") and convert column names to lowercase
voters <- clean_names(voters)
```

```{r}
# Get dimensions of the data frame (rows by columns)
dim(voters)
```

```{r}
# Understand all of the variables using a tidyverse function
glimpse(voters)
```

```{r}
# Understand all of the variables using a base function
str(voters)
```


```{r}
# See the first 6 observations
head(voters)

# See the last 100 observations
tail(voters, n = 100)
```

```{r}
# Look at the full dataset in a separate window
View(voters)
```


Use the following tidyverse functions to explore data:

* `select` - select columns
* `filter` - select rows that match conditions that you provide
* `summarize` - reduce multiple values down to a single value
* `mutate` - create or transform variables
* `group_by` - group by one (or more) variables
* `ungroup` - remove the grouping variables
* `arrange` - reorder rows based upon a variable

```{r}
voters %>% 
  filter(party == "R") %>% 
  arrange(desc(year_of_birth))
```

```{r}
voters_zip_R <- 
  voters %>% 
  filter(party == "R") %>% 
  group_by(home_zipcode) %>% 
  summarize(count = n()) %>%
  ungroup()
```

```{r}
voters %>% 
  # select(year_of_birth, ed, rd, home_zipcode, party, gen_hist_1) %>% 
  group_by(gen_hist_1) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  arrange(desc(count))

voters %>% 
  count(gen_hist_1, sort = T)
```

```{r}
voters %>% 
  count(rd, sort = T)

voters_rd04 <-
  voters %>% 
  filter(rd == "04",
         gen_hist_1 == "2018")
```

```{r}

Sys.Date()

file_name <- paste(Sys.Date(), "voters_rd04.csv", sep = "_")

write_csv(x = voters_rd04,
          path = here("Voters", file_name))

```

# Example of creating a graph

```{r}
voters %>% 
  count(rd, party, name = "count") %>% 
  mutate(rd = fct_reorder(rd, count),
         
         party = case_when(party == "D" ~ "Democrat",
                           party == "R" ~ "Republican",
                           party == "I" ~ "Independent",
                           party == "L" ~ "Libertarian")) %>% 
  ggplot() +
  geom_col(aes(x = rd,
               y = count),
           fill = "red") +
  coord_flip() +
  facet_grid(~ party) +
  theme_minimal()
```

```{r}
crestview <-
  voters %>% 
  filter(str_detect(home_street, "MARKET"),
         str_detect(home_no, "27[0-9]{2}"))
```

```{r}
crest_rd04 <- 
  crestview %>% 
  union(voters_rd04)
```

```{r}
wha <- read_xls(here::here("WHA Properties by Zip and Council.xls"),
                skip = 3) %>% 
  mutate(`Zip Code` = as.character(`Zip Code`))

colnames(wha)
colnames(voters)
```

```{r}
voters_clean_address <- 
  voters %>% 
  mutate(Address = paste(home_no, home_street))
```

```{r}
voters_clean_address %>% 
  left_join(wha, by = c("Address" = "Address",
                        "home_zipcode" = "Zip Code")) %>% 
  filter(! is.na(`Parcel ID`)) %>% 
  select(last_name, first_name, home_no, home_street, `Parcel ID`, `Property Type`, `Council Districts`) %>% 
  count(home_no, home_street, sort = T) %>% 
  mutate(total = sum(n),
         percent = n / total)
```

