---
title: 'Wilmington Voters'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Create filtering of registration sorting by:**

1. ED and RD
2. And also include Wilmington Housing Authority high-rises and properties 
* This would be a separate address list
3. Exclude non-voters by sorting by the date the person last voted with the intent to exclude non-voters (defined as someone who hasn’t voted for 4+ years, meaning if someone last voted in 2014, they’re a non-voter)
* But including those who recently registered since November 2016 but have not had the time to vote in a Presidential election
4. Sort by political party (D, R, and other)
5. Sort by if someone is a consistent primary voter, or only votes in a general election


```{r}
# install.packages("here")
library(here)

# install.packages("tidyverse")
library(tidyverse)

# install.packages("readxl")
library(readxl)

# install.packages("janitor")
library(janitor)
```

```{r}
voters <- read_xlsx(here::here("ActiveFile-Wilm1thru8-20191015.xlsx"))
```

```{r}
voters <- clean_names(voters)
```

